---
title: "Programming Background"
author: "Owen Snyder"
date: '2022-06-09'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../images/")

```

```{r, echo = FALSE, eval = FALSE}
library(rmarkdown)
output_format = "markdown"
output_dir = "/Users/owensnyder/Desktop/st558data/558Blog3"
#output_options = 
keep_html = FALSE
```


## My Programming Experience

In the past, I have only encountered MATLAB, SAS, and R programming languages. I was never formally taught MATLAB or R, so the only legitimate instruction on programming was through ST555 (SAS Programming). I have seen R enough through various classes at NC State and always really enjoyed using it, especially for linear regression techniques taught in ST503. I find R very visually satisfying and user friendly. Also, being able to find more than one solution to a coding "problem" makes learning R a lot less stressful. Conversely, jumping straight into programming with SAS was a little difficult at times and I did not really enjoy how archaic it felt. I think I would still enjoy using it, but if I had a choice I would choose R as my favorite language (already). 

I think the functionality of R makes the language so versatile. For example, simply starting up R and using it as a calculator or an easy way to find probabilities with the built in functions is extremely useful. I also like the ability to make R Markdown documents and all of the features to make your output look exactly how you want it. However, the one aspect I miss in SAS is most of the conditional logic conventions. Using if/then/else in functions has been a challenge for me and I felt it was easier to streamline my conditional logic in SAS easier; however, I'm sure practicing in R will help.

Although I have never formally been taught how to code in R in the way this class is built, it was still a requirement for some courses in the past. It was absolutely necessary to use R in ST503 for building regression models and I thoroughly enjoyed using R as a tool for that. I never struggled with using R in the past but that is mostly because I had not used it in a general data science way. I think that it is not a particularly hard language to learn so far, but definitely requires attention to detail at times.


## Example R Markdown Output
```{r}
plot(iris)

```
